$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-19 paper/e6ssm-tuning-paper.tex
Remove Ellis from name of FT measure.  we cite him thats enough.
Added O(t^2) coefficient for m_{H_u}^2, if time it would be good to check this expression numerically
Substituted several traces into coefficients of g_1^2*g_1'^2*Sigma_1 in O(t^2) coefficients of m_S^2, m_{Q3}^2 and m_{u3}^2 to make the expressions shorter
Added O(t^2) coefficient for m_{H_d}^2
Added O(t^2) coefficient for a_{\lambda}
Added O(t^2) coefficient for a_t
updated paper to include decription of gauge kinetic mixing terms.

apply the traditional Ellis-Barbieri-Giudice measure

@@

% List the derivatives needed in the Taylor series approximation
% to the RGE solutions.

@@

$\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level. The one- and
two-loop RGEs for these parameters may be found in
\cite{Martin:1993zk}. The corresponding $O(t^2)$ contributions are

@@

charges. Two-loop RGEs for the gauge and Yukawa couplings, gaugino
masses and soft trilinears, along with the one-loop RGEs for the soft
scalar masses, were given in \cite{Athron:2009bs} for the particular
case of the E$_6$SSM. At tree level in the EWSB conditions the
parameters that must be considered are $\lambda$, $A_\lambda$,
$m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and $g_1'$. Neglecting kinetic
mixing, the two-loop $\beta$ functions for the relevant gauge couplings read

@@

to denote the trace over the $U(1)'$ charges, along with

@@

b_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaOt2Coeff}

@@

b_{m_{H_d}^2}^{(2)}&=.\label{eq:USSMmHd2Ot2Coeff}

@@

b_{m_{H_u}^2}^{(2)}&=,\label{eq:USSMmHu2Ot2Coeff}

@@

&{}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-\Sigma_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}\nonumber\\
&{}-3Q_L+3Q_Q-6Q_u\big )\Big ]-4Q_Sg_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3\nonumber\\
&{}+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_SM_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMms2Ot2Coeff}

@@

&{}+y_t\left [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\right.\nonumber\\
&{}\left.+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\right ],\label{eq:USSMTYu22BetaOneLoop}\\

@@

b_{a_t}^{(2)}&=.\label{eq:USSMTYu22Ot2Coeff}

@@

&{}+3Q_Q^2-6Q_u^2\big )-\left ( 6Q_Q\Sigma_1+\Sigma_1'\right )\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2+Q_{\overline{H'}}\nonumber\\
&{}-Q_{H'}-3Q_L+3Q_Q-6Q_u\big )\big ]-4Q_Qg_1'^4\big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\

@@

&{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-3Q_1+3Q_2\nonumber\\
&{}+Q_{\overline{H'}}-Q_{H'}-3Q_L+3Q_Q-6Q_u )\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3+3Q_e^2\nonumber\\

>>>>

apply the traditional Barbieri-Giudice measure

@@

@@

$\mu$, $B$, $m_{H_u}^2$, $m_{H_d}^2$ at tree level. For the
renormalisation group running of the relevant parameters
SOFTSUSY uses the one- and two-loop RGEs from
\cite{Barger:1993gh,Martin:1993zk}. The corresponding $O(t^2)$
contributions are

@@

charges.

 Two-loop RGEs for the gauge and Yukawa couplings, gaugino masses and
 soft trilinears, along with the one-loop RGEs for the soft scalar
 masses, were originally obtained in \cite{Athron:2009bs} for the
 particular case of the E$_6$SSM.  FlexibleSUSY uses full one- and
 two-loop RGEs from SARAH, which for the models considered here are
 based on \cite{Martin:1993zk} and the recent extension\footnote{In
   the version of SARAH which we used the extra terms from this
   extension were included for all terms except the trilinear and
   bilinear soft masses. We have been in contact with the SARAH author
   about this and understand they will be included in future
   versions.}  \cite{Fonseca:2011vn} to include models with multiple
 $U(1)$ gauge groups, in the most general case where the trace of the
 matrix formed from the charges $Q^Y_i$ of the $U(1)_Y$ gauge symmetry
 and $Q_i$ of the extra $U(1)^\prime$ symmetry does not vanish,
 i.e.~$\sum_i Q_i^YQ_i \neq 0$.

When this trace is non-zero it will also induce gauge kinetic mixing
to be generated during RGE evolution and this is the case in the
models we consider here \footnote{In E$_6$ inspired models with only
  complete $27$plet matter multiplets this trace would vanish.
  However since we assume some incomplete multiplets so that our
  models are consistent with gauge coupling unification this trace
  doesn't vanish.}. However when these models are evolved down from
the GUT scale the radiatively generated gauge kinetic mixing gives an
off diagonal gauge coupling, $g_{11}$ of just $\approx 0.02$ at the
electroweak scale \cite{King:2005jy} and so it does not play a large
role.  At the same time if gauge kinetic mixing is included the RGE
expressions become very large and unmanageable, so we neglected the
gauge kinetic mixing by setting the SARAH flag NoU1Mixing to true.

%% However for the results we present
%%  here we set the SARAH flag NoU1Mixing to true to avoid generating
%%  unmanageably large expressions.  It has previously been checked that
%%  when these models are evolved down from the GUT scale the radiatively
%%  generated gauge kinetic mixing gives an off diagonal gauge coupling,
%%  $g_{11}$ of just $\approx 0.02$ at the electroweak scale
%%  \cite{King:2005jy} and so it does not play a large role.

At tree level in the EWSB
conditions the parameters that must be considered are $\lambda$,
$A_\lambda$, $m_{H_u}^2$, $m_{H_d}^2$, $m_S^2$ and $g_1$, $g_2$ and
$g_1'$. Neglecting kinetic mixing, the two-loop $\beta$ functions for
the relevant gauge couplings read

@@

to denote the trace over the $U(1)'$ charges, along
with \footnote{This is the trace which is assumed to vanish in
  \cite{Martin:1993zk}.  Although we use the the NoU1Mixing to neglect
  gauge kinetic mixing this is done in SARAH by removing the RGE for
  the off diagonal gauge couplings and effectively setting them to
  zero at all scales by removing all terms involving them from the
  RGEs.  Therefore some terms with this trace remain and the RGEs here
  do not reduce to those which one would obtain from
  \cite{Martin:1993zk} nor those which appear in \cite{Athron:2009bs}.
  Note however these contributions do not appear in the
  corresponding trilinears due to the version of SARAH used. }

@@

b_{a_\lambda}^{(2)}&=\lambda \bigg [ 4\lambda a_\lambda +4\Sigma_{a_\lambda}+6\Sigma_{a_\kappa}+6y_ta_t+6y_ba_b+2y_\tau a_\tau +6g_2^2M_2+\frac{6}{5}g_1^2M_1\nonumber\\
&{}+4g_1'^2M_1'\left ( Q_1^2+Q_2^2+Q_S^2 \right )\bigg ]\times\bigg[2\lambda ^2+2 \Sigma_\lambda +3 \Sigma_\kappa +3 y_t^2+3 y_b^2+y_{\tau }^2-3 g_2^2\nonumber\\
&{}-\frac{3}{5} g_1^2 -2 \left ( Q_1^2 + Q_2^2 + Q_S^2\right )g_1'^2 \bigg]+a_\lambda\bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa \nonumber\\
&{}+6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )+\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\left (2\Sigma_\lambda+3\Sigma_\kappa\right ) \nonumber\\
&{}+3\left ( \frac{15}{2}y_t^4+\frac{15}{2}y_b^4+\frac{3}{2}y_\tau^4 +5y_b^2y_t^2 +3y_b^2y_\tau^2 +y_t^2y_\tau^2\right )\nonumber\\
&{}+\frac{6}{5}g_1^2g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2 \right ) \bigg \}+\lambda \bigg [16\lambda^3a_{\lambda}+16\Pi_{a_\lambda}+24\Pi_{a_\kappa}+8\lambda\sum_{i=1}^3\lambda_i\left ( \lambda_i a_{\lambda}+a_{\lambda_i}\lambda\right )\nonumber\\
&{}+12\lambda\sum_{i=1}^3\kappa_i\left ( \kappa_i a_\lambda + a_{\kappa_i} \lambda\right )+8\sum_{i=1}^3\sum_{j=1}^3\lambda_i\lambda_j\left ( a_{\lambda_i}\lambda_j+\lambda_ia_{\lambda_j}\right )\nonumber\\
&{}+18\sum_{i=1}^3\sum_{j=1}^3\kappa_i\kappa_j\left ( \kappa_i a_{\kappa_j}+a_{\kappa_i}\kappa_j\right )+24\sum_{i=1}^3\sum_{j=1}^3\lambda_i\kappa_j\left ( \lambda_i a_{\kappa_j}+a_{\lambda_i}\kappa_j\right )+72y_t^3a_t+72y_b^3a_b\nonumber\\
&{}+16y_\tau^3a_\tau+12y_ty_b\left ( a_ty_b+y_ta_b\right )+12y_by_\tau\left ( a_by_\tau+y_ba_\tau\right )+30\lambda y_t\left ( a_{\lambda}y_t+\lambda a_t\right )\nonumber\\
&{}+30\lambda y_b\left ( a_{\lambda}y_b+\lambda a_b\right )+10\lambda y_\tau\left ( a_{\lambda}y_\tau+\lambda a_{\tau}\right )-32g_3^2y_t\left ( a_t-y_tM_3\right )-32g_3^2y_b\left ( a_b-y_bM_3\right )\nonumber\\
&{}-32g_3^2\left ( \Sigma_{a_\kappa}-M_3\Sigma_\kappa\right )-12g_2^2\lambda\left ( a_\lambda-\lambda M_2\right )-18g_2^2y_t\left ( a_t-y_tM_2\right )-18g_2^2y_b\left ( a_b-y_bM_2\right )\nonumber\\
&{}-6g_2^2y_\tau\left ( a_\tau-y_\tau M_2\right )-12g_2^2\left ( \Sigma_{a_\lambda}-M_2\Sigma_\lambda \right )-\frac{12}{5}g_1^2\lambda\left ( a_{\lambda}-\lambda M_1\right )-\frac{26}{5}g_1^2y_t\left ( a_t-y_tM_1\right )\nonumber\\
&{}-\frac{14}{5}g_1^2y_b\left ( a_b-y_bM_1\right )-\frac{18}{5}g_1^2y_\tau\left ( a_\tau-y_\tau M_1\right )-\frac{12}{5}g_1^2\left ( \Sigma_{a_\lambda}-M_1\Sigma_\lambda\right )-\frac{8}{5}g_1^2\left ( \Sigma_{a_\kappa}-M_1\Sigma_\kappa\right )\nonumber\\
&{}-8g_1'^2\lambda\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda-\lambda M_1'\right )-12g_1'^2y_t\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )\nonumber\\
&{}-12g_1'^2y_b\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )-4g_1'^2y_\tau\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( a_\tau-y_\tau M_1'\right )\nonumber\\
&{}-8g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( \Sigma_{a_\lambda}-M_1'\Sigma_\lambda \right )-12g_1'^2\left ( Q_S^2+Q_D^2+Q_{\overline{D}}^2\right )\left (\Sigma_{a_\kappa}-M_1'\Sigma_{\kappa}\right )\nonumber\\
&{}+48g_2^4M_2+\frac{576}{25}g_1^4M_1+8g_1'^4M_1'\Sigma_Q\left ( Q_1^2+Q_2^2+Q_S^2\right )\bigg ],\label{eq:USSMTLambdaOt2Coeff}

@@

b_{m_{H_d}^2}^{(2)}&=72y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )+144y_b^2a_b^2+16y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )+32y_\tau^2 a_\tau^2\nonumber\\
&{}+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2 a_\lambda^2+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )\nonumber\\
&{}+6\left ( y_t a_b+y_b a_t\right )^2+12y_b^2y_\tau^2\left ( 2m_{H_d}^2+m_{Q3}^2+m_{d3}^2+m_{L3}^2+m_{e3}^2\right )+12\left ( y_b a_\tau + y_\tau a_b\right )^2\nonumber\\
&{}+6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
&{}+12\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+12\left ( \lambda a_b+y_b a_\lambda\right )^2\nonumber\\
&{}+4\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+4\left ( \lambda a_\tau + y_\tau a_\lambda\right )^2\nonumber\\
&{}+4\sum_{i=1}^3\left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_\lambda\right )^2\right ]\nonumber\\
&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
&{}-32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )-32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
&{}-18g_2^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_2^2\right )-18g_2^2\left ( a_b^2-2y_ba_bM_2\right )\nonumber\\
&{}-6g_2^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_2^2\right )-6g_2^2\left ( a_\tau^2-2y_\tau a_\tau M_2\right )\nonumber\\
&{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
&{}-\frac{14}{5}g_1^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1^2\right )-\frac{14}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )\nonumber\\
&{}-\frac{18}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1^2\right )-\frac{18}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
&{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
&{}-12g_1'^2y_b^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_1^2+Q_Q^2+Q_d^2\right )\times\nonumber\\
&{}\times\left ( a_b^2-2y_b a_b M_1'\right )+6g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( 2Q_1m_{H_d}^2+2Q_1m_{Q3}^2+2Q_1m_{d3}^2+\Sigma_1'\right )\nonumber\\
&{}+12Q_1g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )-4g_1'^2y_\tau^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1'^2\right )\nonumber\\
&{}-4g_1'^2\left ( Q_1^2+Q_L^2+Q_e^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )+2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\times\nonumber\\
&{}\times\left ( 2Q_1m_{H_d}^2+2Q_1m_{L3}^2+2Q_1m_{e3}^2+\Sigma_1'\right )+4Q_1g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )\nonumber\\
&{}+12Q_1g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+12Q_1g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )\nonumber\\
&{}-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )-4g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\times\nonumber\\
&{}\times\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )+2g_1'^2\lambda^2\left ( Q_1+Q_2+Q_S\right )\Sigma_1'+4Q_1g_1'^2\left ( Q_1+Q_2+Q_S\right )\times\nonumber\\
&{}\times\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]+6Q_1g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\times\nonumber\\
&{}\times\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+a_{\kappa_i}^2\right ]-96Q_1g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )\nonumber\\
&{}-72g_2^4M_2^2-12Q_1g_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )\nonumber\\
&{}-\frac{288}{25}g_1^4\left ( \Sigma_1+3M_1^2\right )-\frac{3}{5}g_1^2g_1'^2\Big [ 4Q_1M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2\nonumber\\
&{}+Q_{\overline{H'}}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2\nonumber\\
&{}+Q_{\overline{H'}}^2-Q_{H'}^2-3Q_L^2+3Q_Q^2-6Q_u^2\big )+\left ( \Sigma_1'-2Q_1\Sigma_1\right )\Sigma_Q^Y\Big ]-4Q_1g_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3\nonumber\\
&{}+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )\nonumber\\
&{}+\left ( 6Q_1M_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMmHd2Ot2Coeff}

@@

b_{m_{H_u}^2}^{(2)}&=72y_t^4\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2\right )+144y_t^2a_t^2+8\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )+16\lambda^2a_\lambda^2\nonumber\\
&{}+6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )+6\left ( y_ta_b+y_ba_t\right )^2\nonumber\\
&{}+12\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )+12\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
&{}+6\lambda^2y_b^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{Q3}^2+m_{d3}^2\right )+6\left ( \lambda a_b+y_ba_\lambda\right )^2\nonumber\\
&{}+2\lambda^2y_\tau^2\left ( 2m_{H_d}^2+m_{H_u}^2+m_S^2+m_{L3}^2+m_{e3}^2\right )+2\left ( \lambda a_\tau+y_\tau a_\lambda\right )^2\nonumber\\
&{}+4\sum_{i=1}^3 \left [ \lambda^2\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_{H_d}^2+m_{H_u}^2+2m_S^2\right )+\left ( \lambda a_{\lambda_i}+\lambda_i a_{\lambda}\right )^2\right ] \nonumber\\
&{}+6\sum_{i=1}^3\left [ \lambda^2\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )
+\left ( \lambda a_{\kappa_i}+\kappa_i a_\lambda\right )^2\right ]\nonumber\\
&{}-32g_3^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_3^2\right )-32g_3^2\left ( a_t^2-2y_ta_tM_3\right )\nonumber\\
&{}-18g_2^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_2^2\right )-18g_2^2\left ( a_t^2-2y_ta_tM_2\right )\\
&{}-6g_2^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_2^2\right )-6g_2^2\left ( a_\lambda^2-2\lambda a_\lambda M_2\right )\nonumber\\
&{}-\frac{26}{5}g_1^2y_t^2\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1^2\right )-\frac{26}{5}g_1^2\left ( a_t^2-2y_ta_tM_1\right )\nonumber\\
&{}-\frac{6}{5}g_1^2\lambda^2\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1^2\right )-\frac{6}{5}g_1^2\left ( a_\lambda^2-2\lambda a_\lambda M_1\right )\nonumber\\
&{}-12g_1'^2y_t^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( m_{H_u}^2+m_{Q3}^2+m_{u3}^2+2M_1'^2\right )-12g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2\right )\times\nonumber\\
&{}\times\left ( a_t^2-2y_ta_tM_1'\right )+6g_1'^2y_t^2\left ( Q_2+Q_Q+Q_u\right )\left ( 2Q_2m_{H_u}^2+2Q_2m_{Q3}^2+2Q_2m_{u3}^2+\Sigma_1'\right )\nonumber\\
&{}+12Q_2g_1'^2a_t^2\left ( Q_2+Q_Q+Q_u\right )+12Q_2g_1'^2y_b^2\left ( Q_1+Q_Q+Q_d\right )\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )\nonumber\\
&{}+12Q_2g_1'^2a_b^2\left ( Q_1+Q_Q+Q_d\right )+4Q_2g_1'^2y_\tau^2\left ( Q_1+Q_L+Q_e\right )\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )\nonumber\\
&{}+4Q_2g_1'^2a_\tau^2\left ( Q_1+Q_L+Q_e\right )-4g_1'^2\lambda^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )\nonumber\\
&{}-4g_1'^2\left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )+2g_1'^2\lambda^2\left ( Q_1+Q_2+Q_S\right )\Sigma_1'\nonumber\\
&{}+4Q_2g_1'^2\left ( Q_1+Q_2+Q_S\right )\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+a_{\lambda_i}^2\right ]\nonumber\\
&{}+6Q_2g_1'^2\left ( Q_S+Q_D+Q_{\overline{D}}\right )\sum_{i=1}^3\left [ \kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )+a_{\kappa_i}^2\right ]\nonumber\\
&{}-96Q_2g_3^2g_1'^2M_3^2\left ( 2Q_Q+Q_u+Q_d+Q_D+Q_{\overline{D}}\right )-72g_2^4M_2^2\nonumber\\
&{}-12Q_2g_2^2g_1'^2M_2^2\left ( 9Q_Q+3Q_L+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}\right )+\frac{288}{25}g_1^4\left ( \Sigma_1-3M_1^2\right )\nonumber\\
&{}-\frac{3}{5}g_1^2g_1'^2\Big [ 4Q_2M_1^2\big ( 2Q_d+2Q_{\overline{D}}+2Q_D+6Q_e+3Q_1+3Q_2+Q_{\overline{H'}}+Q_{H'}+3Q_L\nonumber\\
&{}+Q_Q+8Q_u\big )+4M_1'^2\big ( 3Q_d^2+3Q_{\overline{D}}^2-3Q_D^2+3Q_e^2-3Q_1^2+3Q_2^2+Q_{\overline{H'}}^2-Q_{H'}^2\nonumber\\
&{}-3Q_L^2+3Q_Q^2-6Q_u^2\big )-\left ( 2Q_2\Sigma_1+\Sigma_1'\right )\Sigma_Q^Y\Big ]-4Q_2g_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3\nonumber\\
&{}+3Q_e^3+6Q_1^3+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )\nonumber\\
&{}+\left ( 6Q_2M_1'^2-\Sigma_1'\right )\Sigma_Q\Big ],\label{eq:USSMmHu2Ot2Coeff}

@@

&{}+Q_{H'}+3Q_L+Q_Q+8Q_u\big )-\Sigma_1\Sigma_Q^Y\Big ]-4Q_Sg_1'^4\Big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\
&{}+6Q_2^3+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3\big )+\left ( 6Q_SM_1'^2-\Sigma_1'\right )\Sigma_Q\Big ].\label{eq:USSMms2Ot2Coeff}

@@

&{}+y_t\bigg [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\nonumber\\
&{}+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ],\label{eq:USSMTYu22BetaOneLoop}\\

@@

b_{a_t}^{(2)}&=y_t\bigg [ 2\lambda a_\lambda + 12y_ta_t+2y_ba_b+\frac{32}{3}g_3^2M_3+6g_2^2M_2+\frac{26}{15}g_1^2M_1\nonumber\\
&{}+4g_1'^2M_1'\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ]\times\bigg [ \lambda^2+6y_t^2+y_b^2-\frac{16}{3}g_3^2-3g_2^2-\frac{13}{15}g_1^2\nonumber\\
&{}-2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg ]+a_t\bigg \{ 54y_t^4+\frac{13}{2}y_b^4+13y_t^2y_b^2+y_b^2y_\tau^2\nonumber\\
&{}+\lambda^2\left ( \frac{5}{2}\lambda^2+15y_t^2+5y_b^2+y_\tau^2+2\Sigma_\lambda+3\Sigma_\kappa \right )-\frac{16}{3}g_3^2\left ( \lambda^2+2y_b^2+12y_t^2\right )\nonumber\\
&{}-6g_2^2\left ( \lambda^2+y_b^2+6y_t^2\right )-g_1^2\left ( \frac{22}{15}\lambda^2+\frac{4}{3}y_b^2+\frac{52}{5}y_t^2\right )\nonumber\\
&{}+\frac{26}{15}g_1^2g_1'^2\left ( Q_2^2+Q_Q^2+Q_u^2 \right )\bigg \}+y_t\bigg [ 144y_t^3a_t+24y_b^3a_b+14y_ty_b\left ( y_ta_b+a_ty_b\right )\nonumber\\
&{}+2y_by_\tau\left ( y_b a_\tau+a_by_\tau\right )+18\lambda y_t\left ( \lambda a_t+a_{\lambda}y_t\right )+8\lambda y_b\left ( \lambda a_b+a_{\lambda}y_b\right )+2\lambda y_\tau\left ( \lambda a_\tau+a_{\lambda}y_\tau\right )\nonumber\\
&{}+8\lambda^3a_{\lambda}+4\lambda\sum_{i=1}^3\lambda_i\left ( \lambda a_{\lambda_i}+a_{\lambda}\lambda_i\right )+6\lambda\sum_{i=1}^3\kappa_i\left ( \lambda a_{\kappa_i}+a_{\lambda}\kappa_i\right )-64g_3^2y_t\left ( a_t-y_tM_3\right )\nonumber\\
&{}-\frac{32}{3}g_3^2y_b\left ( a_b-y_bM_3\right )-36g_2^2y_t\left ( a_t-y_tM_2\right )-6g_2^2y_b\left ( a_b-y_bM_2\right )-6g_2^2\lambda\left ( a_\lambda-\lambda M_2\right )\nonumber\\
&{}-\frac{52}{5}g_1^2y_t\left ( a_t-y_tM_1\right )-\frac{14}{15}g_1^2y_b\left ( a_b-y_bM_1\right )-\frac{18}{15}g_1^2\lambda \left ( a_\lambda-\lambda M_1\right )\nonumber\\
&{}-24g_1'^2y_t\left ( Q_2^2+Q_Q^2+Q_u^2\right )\left ( a_t-y_tM_1'\right )-4g_1'^2y_b\left ( Q_1^2+Q_Q^2+Q_d^2\right )\left ( a_b-y_bM_1'\right )\nonumber\\
&{}-4g_1'^2\lambda \left ( Q_1^2+Q_2^2+Q_S^2\right )\left ( a_\lambda-\lambda M_1'\right )+48g_2^4M_2+\frac{832}{25}g_1^4M_1\nonumber\\
&{}+8g_1'^4M_1'\Sigma_Q\left ( Q_2^2+Q_Q^2+Q_u^2\right )\bigg ].\label{eq:USSMTYu22Ot2Coeff}

@@

&{}+3Q_Q^2-6Q_u^2\big )-\left ( 6Q_Q\Sigma_1+\Sigma_1'\right )\Sigma_Q^Y\big ]-4Q_Qg_1'^4\big [ 2M_1'^2\big ( 9Q_d^3+9Q_{\overline{D}}^3+9Q_D^3+3Q_e^3+6Q_1^3\nonumber\\

@@

&{}+3Q_L+Q_Q+8Q_u )+\left ( 3Q_u\Sigma_1-2\Sigma_1^\prime\right ) \Sigma_Q^Y\big ]-4Q_ug_1'^4\big [ 2M_1'^2 ( 9Q_d^3+9Q_D^3+9Q_{\overline{D}}^3\nonumber\\
&{}+3Q_e^2+6Q_1^2+6Q_2^2+2Q_{\overline{H'}}^3+2Q_{H'}^3+6Q_L^3+18Q_Q^3+3Q_S^3+9Q_u^3 )\nonumber\\
